Estimating the magnetization distribution within rectangular rock samples

### 2016-06-13 manuscript/manuscript.tex
Regularization part was included

The parameter vector $\mathbf{m} = \mathbf{m}^{\dagger}$ minimizing 
the goal function (equation \ref{eq:goal-function}) is given by
\begin{equation}
\mathbf{m}^{\dagger} = \left( \mathbf{M}^{\top}\mathbf{M} \right)^{-1}
\mathbf{M}^{\top}\mathbf{d} \: ,
\label{eq:estimate}
\end{equation}
where $\mathbf{M}$ is the partitioned matrix defined in equation 
\ref{eq:sensitivity-matrix}.
We consider that the estimated parameter vector $\mathbf{m}^{\dagger}$
given by equation \ref{eq:estimate} approximates the real magnetization 
distribution within the rectangular rock sample.

>>>>

The parameter vector $\mathbf{m} = \mathbf{m}^{\dagger}$ minimizing 
the goal function (equation \ref{eq:goal-function}) is given by
\begin{equation}
\mathbf{m}^{\dagger} = \left( \mathbf{M}^{\top}\mathbf{M} \right)^{-1}
\mathbf{M}^{\top}\mathbf{d} \: ,
\label{eq:estimate}
\end{equation}
where $\mathbf{M}$ is the partitioned matrix defined in equation 
\ref{eq:sensitivity-matrix}.
We consider that the estimated parameter vector $\mathbf{m}^{\dagger}$
given by equation \ref{eq:estimate} approximates the real magnetization 
distribution within the rectangular rock sample. However, solutions given by the equation \ref{eq:estimate} can present non-uniqueness and instability. To overcome this ill- conditioning problem we need to impose a \textit{priori} information. As mentioned before, this procedure is generally called regularization. Here we imposed a constraint using ''Smoothness" regularization, generally called first-order Tikhonov regularization. Then equation \ref{eq:estimate} is now equal to 
\begin{equation}
\mathbf{m}^{\dagger} = \left( \mathbf{M}^{\top}\mathbf{M} + \mu_0 \,  \mathbf{R}^T \mathbf{R}\right)^{-1}
\mathbf{M}^{\top}\mathbf{d} \: ,
\label{eq:estimate_regul}
\end{equation}
where $\mu_0$ is a positive number called parameter regularization and $\mathbf{R}$ is a matrix with elements $-1$ and $1$. For example, if we have a sample formed by two prisms ($P=2$), the matrix $\mathbf{R}$ can be written as

\begin{equation}
\mathbf{R} =\begin{bmatrix}
 1& 0 & 0 & -1 & 0 & 0\\ 
0& 1 & 0 & 0 & -1 & 0\\
 0& 0 & 1 & 0 & 0 & -1\\
\end{bmatrix}_{3P-3 \times 3P}.
\label{eq:matrix_smoothness}
\end{equation}

Generally, the matrix $\mathbf{R}$ is composed by $3P = 3$ rows and $3P$ columns. Each element of the matrix can be described as

\begin{equation}
\left[ \mathbf{R} \right]_{ij} = 
\begin{cases}
1 \: , \quad i = j \\
-1 \: , \quad j = i+3
\end{cases} \: ,
\label{eq:elements_matrix}
\end{equation}
where the others elements of the matrix are zero.
